---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {chunktop}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

Scenario: you've written a report in an R Markdown file, but your collaborator is not an R user. You want to transfer the content of an R Markdown chunk option to them for editing; perhaps something text heavy, like the 'fig.cap' option. They'll return to you the edited text and you want to insert their changes back into the relevant chunk. This is [John's reality](https://fosstodon.org/@johnmackintosh/111047625054222865).

The goal of {chunktop} is to extract the values of selected chunk options, prepare them for external editing, receive the results and reinsert them into the original R Markdown file. It uses [the {parsermd} package](https://cran.r-project.org/package=parsermd) for all the heavy lifting.

Install from GitHub:

```{r install}
if (!require("chunktop")) {
  install.packages("remotes")
  remotes::install_github("matt-dray/chunktop")
}
```

Currently the package will read an Rmd file and extract specific chunk options to a list; convert this data to a data.frame to be saved to CSV; reads in that CSV to a data.frame; and converts it back to a list.

Here's a demo R Markdown file and an Abstract Syntax Tree (AST) of its structure as extracted by {parsermd}.

```{r functions}
path <- system.file("extdata/demo1.Rmd", package = "chunktop")
parsermd::parse_rmd(path)
```

Let's use the {chunktop} functions to extract the options of interest.

```{r chunktop}
(chunktop_list <- get_chunktop(path, c("fig.cap", "eval")))

(chunktop_df <- chunktop_to_df(chunktop_list))
  
csv_file <- tempfile(fileext = ".csv")

write.csv(chunktop_df, csv_file, row.names = FALSE)

(chunktop_df2 <- read.csv(csv_file))

(chunktop_list2 <- df_to_chunktop(chunktop_df2))

(chunktop_df3 <- chunktop_to_df(chunktop_list2))
```
